Finite Property Convex Elicitation Notes

### 2019-01-15 cvx-fin-notes.tex

>>>>

\section{Full Characterization}

\raf{I'm going to give a sequence of equivalent conditions that get farther and farther from the trivial one.
All propositions for now, but eventually we should just take the last statement, chain the proofs, and call it a theorem.}

\raf{NOTE: I'm a bit fuzzy on the terminology surrounding ``embedding'' that we settled on.  Hopefully what I mean is clear enough!}

We begin with a fairly trivial restatement of the definition of embeddability.
\begin{proposition}
  A finite property $\Gamma:\R\toto\P$ is $d$-embeddable if and only if there exists an embedding $\varphi: \R \to \reals^d$ and polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
  \begin{enumerate}
  \item For all $r\in\R, p\in\P$, we have $r\in \Gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
  \item For all $y\in\Y$ there exists some convex function $L_y$ such that for all $r\in\R$ we have $T(r,y) = \partial L_y(r)$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  If $\Gamma$ is $d$-embeddable, we have a convex loss $L$ such that
  \begin{align*}
    r \in \Gamma(p) &\iff \varphi(r) \in \argmin_{r'\in\reals^d} \E_p L(r',Y)\\
                    &\iff 0 \in \partial \E_p L(\varphi(r),Y) \\
                    &\iff 0 \in \sum_y p_y \partial L(\varphi(r),y)~.
  \end{align*}
  Thus, taking $T(r,y) = \partial L(r,y)$ satisfies (1) and trivially (2) with $L_y = L(\cdot,y)$.
  For the converse, we simply take $L(r,y) = L_y(r)$; by condition (1) and the argument above we have exactly that $L$ essentially elicits $\Gamma$.
  \raf{I just realized: we need to justify why we can assume $L$ has polytopical subgradients, vs just polyhedral.  I think this is equivalent to $L$ being finite on all of $\reals^d$, which we can assume, but will probably need machinery from the first part.}
\end{proof}

To further break down conditions (1) and (2), let us state some known results.
First, some notation: let $H_T(v) = \argmax_{x\in T} v\cdot x$ be the support function, \raf{...}
\begin{proposition}
  \raf{I need an assumption here which I don't fully understand, about the presence of facets in at least one polytope.  Basically, if each polytope was lower-dimensional, this doesn't work because they would still have a nonempty Minkowski sum but there wouldn't be any $(d-1)$-faces.  Not sure how to resolve.}
  Let $T_1,\ldots,T_k\subseteq\reals^d$ be polytopes, and $p\in\Delta_k$ be weights.
  Let  $\mathcal{V}$ be the collection of unit normal vectors to all $(d-1)$-faces in $T_1,\ldots,T_k$.
  Then $x \in \sum_{i=1}^k p_i T_i$ if and only if for all nonzero $v\in\mathcal{V}$, we have $v\cdot x \leq \sum_{i=1}^k p_i H_{T_i}(v)$. 
\end{proposition}
\begin{proof}
  \raf{All refs are to the thesis we used (by Weibel).}

  Let $T := \sum_{i=1}^k p_i T_i$.
  By Theorem 3.1.2, every face $F$ of $T$ can be uniquely written as $F = \sum_{i=1}^k p_i F_i$ where $F_i$ is a face of $T_i$.
  By Corollary 3.1.4, $F = \sum_{i=1}^k p_i F_i$ is a face of $T$ if and only if there exists some unit vector $v\in\reals^d$ which is normal to $p_iF_i$ (and thus $F_i$) for all $i$.
  Focusing on the facets

\end{proof}
